The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-24 paper/ms.tex
spelling

% Abstract of the paper
\begin{abstract}
Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 101~stars too bright to have been otherwise observed. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars ordinarily more observed in the nominal \kepler mission. In this Paper, we focus in particular on a subset of these consisting of 60~red giants for which we detect solar-like oscillations. Using high-resolution spectroscopy from the Tillinghast Reflector Echelle Spectrograph (TRES) together with asteroseismic modelling, we constrain the masses and evolutionary states of these benchmark red giants. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and K2, and presented light curves of a small number of variable stars as examples to illustrate this method. In this Paper we present light curves of all unobserved or significantly under-observed stars brighter than $V=8$ in the \kepler field. This sample is biased towards red giants and hot stars, containing only a few FG dwarfs. We find no transiting planets, but detect $M$~new eclipsing binaries, and solar-like oscillations in $N$~red giants. We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability. For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters. Finally, for the oscillating red giants, which constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector Echelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters. We discuss the potential for these as benchmark stars for other stellar surveys, in particular \gaia.

@@

For the whole red giant sample, we have obtained high-resolution spectroscopy with the Tillinghast Reflector Echelle Spectrograph (TRES) in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of \textcolor{red}{something} per resolution element.

>>>>

% Abstract of the paper
\begin{abstract}
Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 101~stars too bright to have been otherwise observed. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars ordinarily more observed in the nominal \kepler mission. In this Paper, we focus in particular on a subset of these consisting of 60~red giants for which we detect solar-like oscillations. Using high-resolution spectroscopy from the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) together with asteroseismic modelling, we constrain the masses and evolutionary states of these benchmark red giants. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and K2, and presented light curves of a small number of variable stars as examples to illustrate this method. In this Paper we present light curves of all unobserved or significantly under-observed stars brighter than $V=8$ in the \kepler field. This sample is biased towards red giants and hot stars, containing only a few FG dwarfs. We find no transiting planets, but detect $M$~new eclipsing binaries, and solar-like oscillations in $N$~red giants. We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability. For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters. Finally, for the oscillating red giants, which constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters. We discuss the potential for these as benchmark stars for other stellar surveys, in particular \gaia.

@@

For the whole red giant sample, we have obtained high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of \textcolor{red}{something} per resolution element.
